### 2016-07-06 case-studies.tex
Source code url added.
edits
Reverted to non-anonymous code.

\vspace*{-4pt}
\section{Case Studies}
\label{sec:case-studies}

We present two case studies below that demonstrate the applicability
of our framework and its practical utility. Both examples
target Ruby-on-Rails applications, which are commonly used to
interface applications to database systems. To analyze these, and
other similar open-source applications, we have developed a symbolic
execution engine that compiles a Rails program to an abstract program
in an extended version of \txnimp, along with some proof automation
support.\footnote{Details can be found in the supplementary material.
  Source code for our implementation, along with applications and
  experiments, are available at the following anonymized url:
  \url{...}} The focus of our formal verification efforts are such
translated \txnimp programs.

>>>>

\section{Case Studies}
\label{sec:case-studies}

We present two case studies below that demonstrate the applicability
of our framework and its practical utility. Both examples
target Ruby-on-Rails applications, which are commonly used to
interface applications to database systems. To analyze these, and
other similar open-source applications, we have developed a symbolic
execution engine that compiles a Rails program to an abstract program
in an extended version of \txnimp, along with some proof automation
support.\footnote{Details can be found in the supplementary material.
Source code of our tools, applications and experiments, is also
provided in the (non-anonymous) supplementary.} The focus of our
formal verification efforts are such translated \txnimp programs.
